### 2025-06-17 basic-statistics.qmd
20250617 - additional documentation

The (sample) variance of $x$ (written as: $s^2$) is calculated as in @eq-variance:

@@

where $x_i$ is each data point, $\bar{x}$ is the mean of $x$, and $n$ is the number of data points.
The population variance divides by $n$ rather than $n-1$ and is written as $\sigma^2$.

The (sample) standard deviation of $x$ (written as: $s$) is calculated as in @eq-sd:

@@

The population standard deviation divides by $n$ rather than $n-1$ and is written as $\sigma$.

>>>>

The ([sample](#sec-sampleVsPopulation)) variance of $x$ (written as: $s^2$) is calculated as in @eq-variance:

@@

where $x_i$ is each data point, $\bar{x}$ is the mean of $x$, and $n$ is the number of data points.
The [population](#sec-sampleVsPopulation) variance divides by $n$ rather than $n-1$ and is written as $\sigma^2$.

The ([sample](#sec-sampleVsPopulation)) standard deviation of $x$ (written as: $s$) is calculated as in @eq-sd:

@@

The [population](#sec-sampleVsPopulation) standard deviation divides by $n$ rather than $n-1$ and is written as $\sigma$.

### 2025-06-17 getting-started.qmd
20250617 - additional documentation

@@

You can learn about a particular function and its arguments by entering a question mark before the name of the function:

@@

A vector is a series of elements that can be numeric or character.
It has one dimension (length).
To create a vector, use the `c()` to combine elements into a vector.
And, we use the assignment operator (`<-`) to assign the vector to an object named `exampleVector`, so we can access it later.

@@

>>>>

You can load a given library using the following syntax:

library("INSERT_PACKAGE_NAME_HERE")
```

For instance, you can use the following code to load the `tidyverse` package [@R-tidyverse]:

@@

A function often takes particular input(s) and produces some form of output.
The name of the function is followed by parentheses; the inputs go in between the parentheses.
You can learn about a particular function and its arguments by entering a question mark before the name of the function:

@@

A vector is a series of elements that can be numeric or character.
It has one dimension (length).
To create a vector, use the `c()` function to combine elements into a vector.
And, we use the assignment operator (`<-`) to assign the vector to an object named `exampleVector`, so we can access it later.
Anything on the right side of an assignment operator gets assigned to the object name on the left side of the assignment operator.

@@

Loops are fine for basic computations, but other approaches (such as the `apply()` family of functions) can be even faster than loops.

### 2025-06-17 simulation.qmd
20250617 - additional documentation

Monte Carlo simulation involves repeated random sampling from a known distribution [@Sigal2016].
For instance, if we know the population distribution for the likely outcomes for a player—e.g., a normal distribution with a known mean (e.g., 150 points) and standard deviation (e.g., 20 points)—we can repeatedly sample randomly from this distribution.

>>>>

Monte Carlo simulation involves repeated random sampling from a known distribution [@Sigal2016].
For instance, if we know the population distribution for the likely outcomes for a player—e.g., a normal distribution with a known mean (e.g., 150 points) and standard deviation (e.g., 20 points)—we can repeatedly sample randomly from this distribution.
The distribution could be, as examples, a normal distribution, a log-normal distribution, a binomial distribution, a chi-square distribution, etc. [@Sigal2016].
The distribution provides a probability density function, which indicates the probability that any particular value would be observed if the data arose from that distribution.
